### 2022-07-18 paper/localpsf.tex
ellipsoid intersection appendix improvements: bounding box precheck

The direct approach to compute $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ is to apply $\Aop$ to a point source centered at $x$ to obtain $\impulseresponse_x$, as per \eqref{eq:impulse_response_delta_action}. Then one can post-process $\impulseresponse_x$ to determine $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$. However, this direct approach is not feasible because we need to know $V(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ before we compute $\phi_x$, in order choose the point $x$. Computing $\phi_x$ in order to determine $V(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ would be extremely computationally expensive, and defeat the purpose of our algorithm, which is to reduce the computational cost by computing impulse responses in batches. Fortunately, it is possible to compute $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ indirectly, \emph{for all points $x\in\Omega$ simultaneously}, by applying $\Aop^T$ to one constant function, $\gdim$ linear functions, and $\gdim(\gdim+1)/2$ quadratic functions (e.g., 6 total operator applies in two spatial dimensions and 10 in three spatial dimensions). This may be motivated by analogy to matrices. If $\mathbf{B}\in \mathbb{R}^{\fedim \times \fedim}$ is a matrix with $i^\text{th}$ column $\mathbf{b}_i$ and $\mathbf{f} \in \mathbb{R}^\fedim$, then
\begin{equation*}
\mathbf{B}^T \mathbf{f} = \begin{bmatrix}
\horzbar & \mathbf{b}_1^T & \horzbar \\
\horzbar & \mathbf{b}_2^T & \horzbar \\
& \vdots & \\
\horzbar & \mathbf{b}_\fedim^T & \horzbar
\end{bmatrix}
\mathbf{f} = 
\begin{bmatrix}
\mathbf{b}_1^T \mathbf{f} \\
\mathbf{b}_2^T \mathbf{f} \\
\vdots \\
\mathbf{b}_\fedim^T \mathbf{f}
\end{bmatrix}.
\end{equation*}
By computing one matrix-vector product of $\mathbf{B}^T$ with $\mathbf{f}$, we compute the inner product of each column of $\mathbf{B}$ with $\mathbf{f}$ simultaneously. The operator case is analogous, with the impulse response $\phi_x$ taking the place of a matrix column. We have
\begin{equation}
\label{eq:operator_simultaneous_ips}
\left(\Aop^T f\right)^*(x) = \int_\Omega K(y,x) f(y) dy = \left(\phi_x, f\right)_{L^2(\Omega)}.
\end{equation}
By computing one operator application of $\Aop^T$ to $f$, we compute the inner product of each impulse response $\phi_x$ with $f$, for all points $x$ simultaneously.

@@

>>>>

The direct approach to compute $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ is to apply $\Aop$ to a point source centered at $x$ to obtain $\impulseresponse_x$, as per \eqref{eq:impulse_response_delta_action}. Then one can post-process $\impulseresponse_x$ to determine $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$. However, this direct approach is not feasible because we need to know $V(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ before we compute $\phi_x$, in order choose the point $x$. Computing $\phi_x$ in order to determine $V(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ would be extremely computationally expensive, and defeat the purpose of our algorithm, which is to reduce the computational cost by computing impulse responses in batches. Fortunately, it is possible to compute $\spatialvol(x)$, $\spatialmean(x)$, and $\spatialcov(x)$ indirectly, \emph{for all points $x\in\Omega$ simultaneously}, by applying $\Aop^T$ to one constant function, $\gdim$ linear functions, and $\gdim(\gdim+1)/2$ quadratic functions (e.g., 6 total operator applies in two spatial dimensions and 10 in three spatial dimensions). This may be motivated by analogy to matrices. If $\mathbf{B}\in \mathbb{R}^{\fedim \times \fedim}$ is a matrix with $i^\text{th}$ column $\mathbf{b}_i$ and $\mathbf{f} \in \mathbb{R}^\fedim$, then
\begin{equation*}
\mathbf{B}^T \mathbf{f} = \begin{bmatrix}
\horzbar & \mathbf{b}_1^T & \horzbar \\
\horzbar & \mathbf{b}_2^T & \horzbar \\
& \vdots & \\
\horzbar & \mathbf{b}_\fedim^T & \horzbar
\end{bmatrix}
\mathbf{f} = 
\begin{bmatrix}
\mathbf{b}_1^T \mathbf{f} \\
\mathbf{b}_2^T \mathbf{f} \\
\vdots \\
\mathbf{b}_\fedim^T \mathbf{f}
\end{bmatrix}.
\end{equation*}
By computing one matrix-vector product of $\mathbf{B}^T$ with $\mathbf{f}$, we compute the inner product of each column of $\mathbf{B}$ with $\mathbf{f}$ simultaneously. The operator case is analogous, with the impulse response $\phi_x$ taking the place of a matrix column. We have
\begin{equation}
\label{eq:operator_simultaneous_ips}
\left(\Aop^T f\right)^*(x) = \int_\Omega \Aker(y,x) f(y) dy = \left(\phi_x, f\right)_{L^2(\Omega)}.
\end{equation}
By computing one operator application of $\Aop^T$ to $f$, we compute the inner product of each impulse response $\phi_x$ with $f$, for all points $x$ simultaneously.

@@

We may further reduce the cost of performing many ellipsoid intersection tests by first checking whether the coordinate axis aligned bounding boxes for the ellipsoids intersect. Checking whether two axis-aligned bounding boxes intersect is extremely cheap. If the bounding boxes do not intersect, then the ellipsoids do not intersect, so no further action is necessary. If the bounding boxes do intersect, the ellipsoids may or may not intersect, so one must perform the more expensive ellipsoid intersection test described above
